\documentclass[xcolor=svgnames,table,aspectratio=169]{beamer}
\usepackage{musicslides}

\newcommand{\name}{In Christ Alone}  % TITLE
\newcommand{\composer}{Keith Getty, Stuart Townend}  % COMPOSER
\renewcommand{\year}{2001}  % YEAR OF PUBLISHING
\newcommand{\publisher}{Thankyou Music}  % PUBLISHER(S)
\newcommand{\ccli}{3350395}  % CCLI

\renewcommand{\cite}{\bottomleft{``\name'' by \composer\\\textcopyright\year\ \publisher\\CCLI License \#\ccli\\}}
\renewcommand{\header}{\topleft{\name}}

\begin{document}
\begin{frame}
\header
\begin{center}
In Christ alone my hope is found,

He is my light, my strength, my song;

This Cornerstone, this solid Ground,

Firm through the fiercest drought and storm.

What heights of love, what depths of peace,

When fears are stilled, when strivings cease!

My Comforter, my All in All,

Here in the love of Christ I stand.
\end{center}
\cite
\end{frame}

\begin{frame}
\header
\begin{center}
In Christ alone! – who took on flesh,

Fullness of God in helpless babe.

This gift of love and righteousness,

Scorned by the ones He came to save:

Till on that cross as Jesus died,

The wrath of God was satisfied –

For every sin on Him was laid;

Here in the death of Christ I live.
\end{center}
\end{frame}

\begin{frame}
\header
\begin{center}
There in the ground His body lay,

Light of the world by darkness slain:

Then bursting forth in glorious day

Up from the grave He rose again!

And as He stands in victory

Sin’s curse has lost its grip on me,

For I am His and He is mine-

Bought with the precious blood of Christ.
\end{center}
\end{frame}

\begin{frame}
\header
\begin{center}
No guilt in life, no fear in death,

This is the power of Christ in me;

From life’s first cry to final breath,

Jesus commands my destiny.

No power of hell, no scheme of man,

Can ever pluck me from His hand:

Till He returns or calls me home,

Here in the power of Christ I’ll stand.
\end{center}
\end{frame}

\end{document}
