\documentclass[9pt]{extarticle}

\usepackage{chordsheet}
    
% SET THESE FOR THE SONG
\newcommand{\name}{In Christ Alone} % TITLE
\newcommand{\ccli}{3350395} % CCLI
\newcommand{\composer}{Keith Getty, Stuart Townend} % COMPOSER
\newcommand{\bpm}{63} % BEATS PER MINUTE
\newcommand{\timesignature}{4/4} % TIME SIGNATURE
\newcommand{\key}{B Major} % KEY OF SONG
\newcommand{\bibleverse}{Isaiah 28:16, Philippians 4:7, 13} % BIBLE VERSE REFERENCE
\newcommand{\arranger}{ACF Worship} % ARRANGER
    
\fancyhead[L]{ \\ \bpm\ bpm, \timesignature \\ \key}
\fancyhead[C]{{\Large \bf{\name}} \\ \#\ccli \\ \bibleverse}
\fancyhead[R]{ \\ \composer \\ \arranger}

\begin{document}
\bsong

\bv
In \c{E}Christ a\c{B}lone my \c{E}hope is \c{F\s }found,

\c{B}He is my \c{E}light, my \c{F\s }strength, my \c{B}song;

This \c{E}Corner\c{B}stone, this \c{E}solid \c{F\s }Ground,

\c{B}Firm through the \c{E}fiercest \c{F\s }drought and \c{B}storm.

What heights of \c{E}love, what \c{B}depths of \c{F\s }peace,

When \c{B/D\s }fears are \c{E}stilled, when \c{B}strivings \c{F\s }cease!

My \c{E}Comfor\c{B}ter, my \c{E}All in \c{F\s }All,

\c{B}Here in the \c{E}love of \c{F\s }Christ I \c{B}stand.
\ev

\bv
In \c{E}Christ a\c{B}lone! – who \c{E}took on \c{F\s }flesh,

\c{B}Fullness of \c{E}God in \c{F\s }helpless \c{B}babe.

This \c{E}gift of \c{B}love and \c{E}righteous\c{F\s }ness,

\c{B}Scorned by the \c{E}ones He \c{F\s }came to \c{B}save:

Till on that \c{E}cross as \c{B}Jesus \c{F\s }died,

The \c{B/D\s }wrath of \c{E}God was \c{B}satis\c{F\s }fied –

For \c{E}every \c{B}sin on \c{E}Him was \c{F\s }laid;

\c{B}Here in the \c{E}death of \c{F\s }Christ I \c{B}live.
\ev

\bv
There \c{E}in the \c{B}ground His \c{E}body \c{F\s }lay,

\c{B}Light of the \c{E}world by \c{F\s }darkness \c{B}slain:

Then \c{E}bursting \c{B}forth in \c{E}glorious \c{F\s }day

\c{B}Up from the \c{E}grave He \c{F\s }rose a\c{B}gain!

And as He \c{E}stands in \c{B}victo\c{F\s }ry

Sin’s \c{B/D\s }curse has \c{E}lost its \c{G\s m}grip on \c{F\s }me,

For \c{E}I am \c{B}His and \c{E}He is \c{F\s }mine-

\c{B}Bought with the \c{E}precious \c{F\s }blood of \c{B}Christ.
\ev

\bv
No \c{E}guilt in \c{B}life, no \c{E}fear in \c{F\s }death,

\c{B}This is the \c{E}power of \c{F\s }Christ in \c{B}me;

From \c{E}life’s first \c{B}cry to \c{E}final \c{F\s }breath,

\c{B}Jesus com\c{E}mands my \c{F\s }desti\c{B}ny.

No power of \c{E}hell, no \c{B}scheme of \c{F\s }man,

Can \c{B}ever \c{E}pluck me \c{B}from His \c{F\s }hand:

Till \c{E}He re\c{B}turns or \c{E}calls me \c{F\s }home,

\c{B}Here in the \c{E}power of \c{F\s }Christ I’ll \c{B}stand.
\ev

\esong

\end{document}
